Efficient Parallelization of $\ell_1$-Minimization for Face Recognition \thanks{Corresponding author: . This work was partially supported by ARO MURI W911NF-06-1-0076.}

### 2011-02-14 paper/main.tex
Added proof of concept for getting latex into diagrams.

@@

\begin{figure}
\centering
\includegraphics[width=3.5in]{figures/pipeline.pdf}
\caption{The Full Recognition Pipeline}
\label{fig:pipeline}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=3.5in]{figures/alignment_l1.pdf}
\caption{Alignment Stage L1 Solver}
\label{fig:alignment_l1}
\end{figure}

@@

In order to adapt the general algorithm to face alignment and recognition, we formulated the 
$\ell_1$-minimization problem as ___ as described in [book].

@@

\begin{figure}
\centering
\includegraphics[width=3.5in]{figures/runtime_graph.pdf}
\caption{GPU Alignment Stage Time vs. Size of Database}
\label{fig:alignment_runtime}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=3.5in]{figures/PALM_benchmark_ratio_1.png}
\caption{This is where the caption goes.}
\label{fig:uniqueidentifierforthisimage}
\end{figure*}

>>>>

% Needed for getting formulas in dia diagrams.
\usepackage{pstricks}
\usepackage{tikz}

@@

\begin{figure}
\centering
%\includegraphics[width=3.5in]{figures/pipeline.pdf}
\input{figures/pipeline.tex}
\caption{The Full Recognition Pipeline}
\label{fig:pipeline}
\end{figure}

%\begin{figure}
%\centering
%\includegraphics[width=3.5in]{figures/alignment_l1.pdf}
%\caption{Alignment Stage L1 Solver}
%\label{fig:alignment_l1}
%\end{figure}

@@

In order to adapt the general algorithm to face alignment and recognition, we formulated the 
$\ell_1$-minimization problem as described in \cite{}.

@@

%\begin{figure}
%\centering
%\includegraphics[width=3.5in]{figures/runtime_graph.pdf}
%\caption{GPU Alignment Stage Time vs. Size of Database}
%\label{fig:alignment_runtime}
%\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=3.5in]{figures/PALM_benchmark_ratio_1}
\caption{This is where the caption goes.}
\label{fig:uniqueidentifierforthisimage}
\end{figure*}
